Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-10 ms.tex
zakamska

Thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$.  Conduction may, however, offset the effects of radiative cooling in making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).

>>>>

Thermal conduction, by contrast, results in only order unity changes
to our results for the stagnation radius (and hence the accretion
rate) for our fiducial value of the saturation parameter $\phi =0.1$.
% Conduction may, however, offset the effects of radiative cooling in
% making the flow more thermally stable
% (e.g.~\citealt{Zakamska&Narayan03}).
